### 2024-09-30 article_codes.qmd
Correct typos and links to figures/tables

We have used the Corine Land Cover 2018 (Version 2020_20u1), downloaded from [Copernicus](https://land.copernicus.eu/pan-european/corine-land-cover). The resolution of the raster is 100 m x 100 m. We classify as potential wildland vegetation the following classes @fig-corine-wild-vegetation:

@@

Original data from [@Aragoneses2022] and we considered all fuels. The resolution of the original map is 1km , so we have re-sampled it to a grid cell of 250x250 metres (same than `region_r`) based in the type that is most presented in the area; i.e., `mode`.

@@

Valuer by counties: @tbl-summary-wui-county):

>>>>

We have used the Corine Land Cover 2018 (Version 2020_20u1), downloaded from [Copernicus](https://land.copernicus.eu/pan-european/corine-land-cover). The resolution of the raster is 100 m x 100 m. We classify as potential wildland vegetation the following classes @fig-corine-fuel-map-norway:

@@

We use the fuel map produced by [@Aragoneses2022]. The original resolution of the map is 1km, so we resampled it to a grid cell of 250x250 metres (same grids than `region_r`) based in the type that is most presented in the area; i.e., `mode` (@fig-firEUrisk-fuel-map-norway).

@@

Values by counties:
